Adaptive Test

### 2023-10-11 scripts/validation_ML_estimator.Rmd
add plot to rmd

---
title: "Adaptive Test"
output:
  word_document:
    toc: no
  pdf_document: 
    keep_tex: yes
#header-includes:
#documentclass: apa7
#classoption: doc
bibliography: references.bib
csl: apa.csl
editor_options:
  markdown:
    wrap: sentence
---

@@

After that, open an R IDE of your choice and install the required R packages with `renv::restore()`.

@@

To verify maximum likelihood estimation, the script `generate_data.R` will use the package `catR` [@magis2012] to generate 500 item banks and corresponding response patterns for an ability level of 0.
These will be saved as JSON files in the `generated` directory.

The corresponding JavaScript file `ability_estimation.test.js` in the folder `lib` will load the item banks and response patterns to run the ability estimation algorithm.
The result is then compared to `catR` [@magis2012] using the testing framework `Jest` [@jestjs/j2023].
The tests will succeed if the difference between the ability estimation result and the estimation from `catR` is close to 0.

@@

@@

::: {#refs}
:::

>>>>

---
title: "Adaptive Test"
output: pdf_document
editor_options:
  markdown:
    wrap: sentence
---

@@

After that, open an R IDE of your choice and install the required R packages with `renv::restore()`.
Please ensure to set the working directory to the `validate_ML_est` folder.

@@

To verify maximum likelihood estimation, the script `generate_data.R` will use the package `catR` (Magis and Raîche 2012) to generate 500 item banks and corresponding response patterns for an ability level of 0.
These will be saved as JSON files in the `generated` directory.

The corresponding JavaScript file `ability_estimation.test.js` in the folder `lib` will load the item banks and response patterns to run the ability estimation algorithm.
The result is then compared to `catR` (Magis and Raîche 2012) using the testing framework `Jest` (*Jestjs/Jest* 2023).
The tests will succeed if the difference between the ability estimation result and the estimation from `catR` is close to 0.

@@

The following plot shows the estimations errors when comparing our maximum likelihood estimation implementation with `catR`.

![](images/error_plot.png)

@@

*Jestjs/Jest*.
2023.
Jest.
<https://github.com/jestjs/jest>.

Magis, David, and Gilles Raîche.
2012.
"Random Generation of Response Patterns Under Computerized Adaptive Testing with the R Package catR." *Journal of Statistical Software* 48 (8).
<https://doi.org/10.18637/jss.v048.i08>.
